\documentclass[11pt]{res} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document} 
 
\name{Jeremy A. Cantú\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf Current Address} \\   Austin, TX
         78747  \\ (956)286-8386}
\address{{\bf Contact Information} \\ jeremycantu.com \\ github.com/jac21 \\ mail@jeremycantu.com}
 
                                             
\begin{resume}
                                               
 
\section{Objective and Summary}
   Jeremy originally hails from the border town of Laredo, Texas, thereafter attending Texas A\&M University in College Station wherein he earned his bachelor's degree in Computer Science with a concentration in Systems Engineering. He has an avid interest in building distributed, scalable, and performant back-end systems with a focus on delivering clean, quality solutions whilst evangelizing those same standards amongst his peers.
 
\section{Work Experience}

Manager, Software Development \& Engineering \\
Charles Schwab \\
May 2024 - Present

Software Development Engineer Senior Specialist \\
Charles Schwab \\
April 2019 - May 2024
\vspace{0.2in}
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Led globally distributed teams in the architecture, development, and performance tuning of critical financial technology applications and batch services supporting the Schwab Portfolio Performance Reporting platform impacting nearly 40 million clients, utilizing .NET C\#, WebAPI, and the NoSQL database Aerospike in an Agile and private cloud-based environment. 
\newline
    \item In addition to the above, took lead in bringing SOLID design principles, unit and integration testing, memory profiling, and performance benchmarking to the forefront of associated teams' day-to-day delivery activities. Much of this was facilitated via a self-driven technical forum that radiated these best practices across the organization and our offshore counterparts.
 \end{itemize}

Software Developer \\
Advanced Solutions International \\
January 2017 - March 2019
\vspace{0.2in}
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Full-stack, .NET-oriented software developer, specializing in C\#, JavaScript, HTML5, and CSS3 based web-development, including back-end (Entity Framework, T-SQL) and RESTful API (WebAPI) middle-ware technologies, facilitated within an Agile, Scrum-based environment.
\newline
    \item Crafted and performed quarterly product penetration-testing involving vulnerability scanning tools such as Arachni and Burp Suite, as well as database injection tools such as SQLMap.
 \end{itemize}

 Software Developer \\
Dell \\
April 2016 - January 2017
\vspace{0.2in}
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Software Developer Engineer in Test, as part of the Dell Consumer Services "Responsive Platform" team. Responsible for automated test framework and suite creation for the entirety of the application, utilizing C\#, Selenium WebDriver, and SpecFlow, as well as monitoring and analysis using Splunk and Adobe Analytics.
 \end{itemize}
 
 
IT Consultant \\
Sogeti \\
June 2015 - April 2016
\vspace{0.2in}
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Microsoft-technology oriented software developer, responsible for client-site projects in varying domains, platforms and technologies. 
\newline
   \item Major accomplishments include a role as a Software Development Engineer in Test at Dell (took part in creating automated test suites for customer support applications using Selenium Webdriver and Protractor.NET, among other .NET and C\# technologies), as well as leading the Summer 2015 graduating class as the "Class President," elected by his fellow co-workers and peers.
 \end{itemize}

\section{Current Skillset} 
 
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Languages: Proficiency in .NET C\# (10) and JavaScript (ES5, ES6)
\\
   \item Front-end Web Development: Proficiency with HTML5, CSS3, NPM dependency management, experience with the Angular framework and React library
\\
    \item Back-end Web Development: Proficiency in .NET stacks involving ASP.NET WebAPI, Entity Framework and T-SQL, NoSQL data-store Aerospike, experience with JavaScript stacks involving Node.js. Proficiency in performance tuning, parallelism, and concurrency concepts alongside profiling toolsets.
 \end{itemize}
 
\section{Education} 
 \noindent Texas A\&M University, College Station, Texas - May 2015 \\
B.S. Computer Science, Systems Engineering Track \\
Relevant Courses: Design and Analysis of Algorithms, Distributed Objects Programming, Networks and Distributed Programming
 
\section{Professional Certifications} 
 \noindent Cloud Digital Leader \\
Google Cloud \\
Issued: November 18th, 2023 \\
Expires: November 18th, 2026

\end{resume}
\end{document}











